### 2025-01-28 paper/icml25/first/sects/abstract.tex
few corrections...
minor on abstract and main contribution

\begin{abstract}
Reinforcement learning algorithms have demonstrated success in domains such as robotics and multi-agent systems, 
yet they often exhibit limited sample efficiency in complex environments, 
and a unified approach that effectively addresses both single- and multi-agent settings remains elusive.
To challenge this gap, we introduce a novel framework, \fname{}, inspired by SHAC, which is a reinforcement learning algorithm designed for differentiable simulators. Unlike SHAC, \fname{} eliminates the requirement for differentiable transition and reward functions by utilizing plain neural networks to estimate the gradients that would otherwise be derived directly from simulators. These neural networks are trained alongside the policy and value networks of SHAC. We evaluate \fname{} on a set of challenging multi-agent scenarios from VMAS and compare its performance against SHAC and PPO---a current state-of-the-art algorithm for non-differentiable environments. Our results demonstrate that \fname{} significantly outperforms PPO and achieves comparable performance to SHAC, despite not having access to simulator gradients.
\end{abstract}

>>>>

\begin{abstract}
Reinforcement learning algorithms have demonstrated success in domains such as robotics and multi-agent systems, 
yet they often exhibit limited sample efficiency in complex environments, 
and a unified approach that effectively addresses both single- and multi-agent settings remains elusive.
To challenge this gap, we introduce a novel framework, \fname{}, inspired by SHAC, which is a reinforcement learning algorithm designed for differentiable simulators. Unlike SHAC, \fname{} eliminates the requirement for differentiable transition and reward functions by utilizing plain neural networks to estimate the gradients that would otherwise be derived directly from simulators. These neural networks are trained alongside the policy and value networks of SHAC\@. We evaluate \fname{} on a set of challenging multi-agent scenarios from VMAS and compare its performance against SHAC and PPO---a current state-of-the-art algorithm for non-differentiable environments. Our results demonstrate that \fname{} significantly outperforms PPO in both single- and multi-agent scenarios and achieves comparable performance to SHAC, despite not having access to simulator gradients.  
\end{abstract}

### 2025-01-28 paper/icml25/first/sects/shacpp.tex
minor on fig 1
minor on abstract and main contribution

\begin{figure*}[t]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/shac.pdf}
        \caption{SHAC}%
        \label{fig:shac}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/shacpp.pdf}
        \caption{\fname{}}%
        \label{fig:shacpp}
    \end{subfigure}
    \caption{Comparison between SHAC and \fname{}. Nodes with labels (such as $r_i$ or $r'_i$) values. Nodes without labels (such as $\pi$ or $R$) represent functions. Dashed lines are used to represent non differentiability. $a_i$ and $r_i$ represent the collection of actions and rewards for all agents}\label{fig:shac-shacpp}
\end{figure*}

@@

In practice, this is achieved by leveraging a \emph{replay buffer} to cache the state-action-reward triplets obtained from the environment. The neural network is then trained to minimize the mean squared error (MSE) loss. Specifically, we minimize the loss $\mathcal{L}_\theta^{\rewards{i}}:(\states\times\actions{i}\times\states)^N\rightarrow\mathbb{R}$:
$$ \mathcal{L}_\theta^{\rewards{i}}(\batch) = \frac{1}{\bs}\sum_{s,a,s',r \in \batch}\left( {\rewards{i}}_\theta(s, a) - r \right)^2 $$
Where $B$ represents a batch of state-action-state-reward tuples sampled uniformly from the cache.

>>>>

\begin{figure*}[t]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/shac.pdf}
        \caption{SHAC}%
        \label{fig:shac}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/shacpp.pdf}
        \caption{\fname{}}%
        \label{fig:shacpp}
    \end{subfigure}
    \caption{
        Comparison between SHAC and \fname{} during a rollout of 4 steps.
        Nodes with labels (such as $r_i$ or $r'_i$) values. Nodes without labels (such as $\pi$ or $R$) represent functions. Dashed lines are used to represent non differentiability. $a_i$ and $r_i$ represent the collection of actions and rewards for all agents}\label{fig:shac-shacpp}
\end{figure*}

@@

In practice, this is achieved by leveraging a \emph{replay buffer} to cache the state-action-reward triplets obtained from the simulator. The neural network is then trained to minimize the mean squared error (MSE) loss. Specifically, we minimize the loss $\mathcal{L}_\theta^{\rewards{i}}:(\states\times\actions{i}\times\states)^N\rightarrow\mathbb{R}$:
$$ \mathcal{L}_\theta^{\rewards{i}}(\batch) = \frac{1}{\bs}\sum_{s,a,s',r \in \batch}\left( {\rewards{i}}_\theta(s, a) - r \right)^2 $$
Where $B$ represents a batch of state-action-state-reward tuples sampled uniformly from the cache.
